---
title: "Eating Out"
author: "Jonathan Urbano"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
#require(haven)
require(foreign)
```

```{r, eval=TRUE,warning=FALSE}
#GSS <-(read_dta(file="GSS1998.dta))
GSS<- readstata13::read.dta13(file="GSS1998.dta")
GSS <-droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <-na.omit(mydata)
```







```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

In the % wise there was no much difference % in eating out from black and other race.The white were eating out more.




```{r}
dd2 <- mydata %>% group_by(race,eatout) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=race,y=count,fill=eatout))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=race,y=prcnt*100,fill=eatout)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


The one on the left is by count and the one in the right is by %







```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
We have numerical result % is the top table the white people are in out. Almost 70% black were eating out, and 28 people eat in. The other race were the smallest and the black is in the middle, just the white group was was eating out more and had the highest %.







```{r}
chisq.test(table1)
chisqtestGC(table1)
```
We have a low p value .000002287. The Chi-square statistics s is 25.9769







```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```
The p value of white is greater than 0.05. The p value is lower for black . The white and the black have difference of 2.2 eating out. Fisher xy is the analog to tuki HD. The odds between black and white is somewhere were 0 is between 0.4 and 1.49 and zero is in the middle. this two methods are very similar to each other.







